---
title: "Title"
author: "Authors"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
    # Agergar este exe en el folder de pandoc pa manejar cross references
    pandoc_args: ["-Fpandoc-crossref"]
bibliography: Library.bib
csl: remote-sensing.csl
editor_options: 
  markdown: 
    wrap: 72
---

---
figureTitle: "Figure"
tableTitle: "Table"
equationTitle: "Equation"
eqnPrefix: "equation"
figPrefix: 
  - "fig."
  - "figs."
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(tidymodels)
library(randomForest)
library(yardstick)
library(glue)
library(vip)
library(rstatix)
library(lemon)
library(flextable)
library(magick)
library(grid)

# Flextable options
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 12, 
  theme_fun = function(x) theme_booktabs(x,bold_header = TRUE),
  padding = 6,
  background.color = "#FFFFFF",
  digits = 2,
  decimal.mark = ".",
  big.mark = ",",
  na_str = "-")

knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)

# change figure units to cm
chunkhooks::hook_figure_unit("cm")

# Auto figure and table number
figure_f = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('Figure ', i, '. ', x, sep = '')
  }
})

table_f = local({
  j = 0
  function(x) {
    j <<- j + 1
    paste('Table ', j, '. ', x, sep = '')
  }
})
```

# Introduction

Text and citations [@Lugo1990; @Ainslie2002]. 

# Methods

## Study site

Figure from file

```{r fig1, echo= FALSE, warning=FALSE, message = FALSE,fig.width=16, fig.height=10, fig.cap = figure_f("Location of the study site and sampled plots")}
#| crop: true

img <- image_read("D:/Drive/Jonathan_trabaggio/Doctorado/R/CometaLiDARrevML/Map/Map1.jpeg")
img |> 
  grid::grid.raster()
```

## Data

Equations and cross reference
@eq:eqn1:

$$AGB = 0.0673( \rho DBH^2H)^{0.976}$${#eq:eqn1}

in line equations or terms $\rho$ 

# Results

inline code
`r round(mean(df$AGB), 2)` Mg/ha.

Example of table with flextable

```{r tablefield, echo= FALSE}
df_compl |>
  dplyr::select(Sitio, Altura.promedio, SumaAGB_ha, sdAGB) |>
  dplyr::arrange(SumaAGB_ha) |>
  flextable() |>  
  set_header_labels(Sitio = "Plot", 
                    Altura.promedio = "Mean height (m)", 
                    SumaAGB_ha = "AGB (Mg/ha)", 
                    sdAGB = "sdAGB (Mg/ha)") |>
  colformat_double() |>
  set_caption(
    as_paragraph(
      as_chunk(table_f("Structural attributes of the sampled plots"))
    ), word_stylename = "Table Caption"
  ) %>%
  set_table_properties(layout = "autofit")
```

Example of figure created directly in the file.

```{r fig2, echo= FALSE, warning=FALSE, message = FALSE,fig.width=16, fig.height=10, fig.cap = figure_f("AGB and its uncertainty in the sampled plots.")}
#| crop: true
df_compl |>
  mutate(across(Dens_ha, ~.x*1250/10000)) |>
  ggplot(aes(x = SumaAGB_ha, 
             y = sdAGB,
             col = as.factor(Sitio), 
             # ymin = IC2.5,
             # ymax = IC97.5
             )) + 
  geom_point(show.legend = FALSE,
             size = 2,
             position=position_dodge(width=0.5)) +
  # geom_errorbar(show.legend = FALSE,
  #               lwd = 1,
  #               position=position_dodge(width=0.5)) +
  # geom_abline(slope = 0.1, intercept = 0) +
  scale_x_continuous(expand = c(0.1,0.1)) +
  scale_y_continuous(expand = c(0.1,0.1)) +
  labs(x = "AGB (Mg/ha)", 
       y = "sdAGB (Mg/ha)") + 
  cowplot::theme_cowplot() + 
  theme(
    text=element_text(size=20,colour="black"),
    axis.text = element_text(size=20, colour="black", angle = 90, hjust = 1, vjust = 0.5), 
    axis.title = element_text(size=20, colour="black", face = "bold"), axis.line = element_line(colour = "black"))
```

# Discussion

# Conclusion

# References
